Working with Code environments in texor

### 2023-08-19 supplement/code-env/code-example.tex
edits to figure-env supplement

Code Environment types are summarized in Table \ref{table:1}.

@@

% Code in Figures
\section{Code in Figure Environments}
A small example of code in a figure environment is demonstrated in Figure \ref{code:example} (named CodeBlock \ref{code:example} in the HTML). This is a common practice
in R News articles as it used to add a boxed border around the code which looks 
attractive. However, in web articles there isn't much advantage to it.

@@

Table \ref{table:2} is an example of code environments within a table.

@@

A similar arrangement can be used to arrange figures/plots besides code environments.
Table \ref{table:3} demonstrates a table with code and a figure.
\begin{table}[htbp]
  \centering
  \begin{tabular}{| c | c |}
  \hline
  Code & Plot\\
    \hline
    \begin{minipage}{0.45\textwidth}
\vspace{1mm}
\begin{example}
x <- 1:100
y <- dbinom(x,100,prob = 0.5)
plot(x,y)
\end{example}
    \end{minipage} &
    \begin{minipage}{0.45\textwidth}
    \centering
    \includegraphics[width=1\textwidth]{binom}
    \end{minipage}\\
    \hline
  \end{tabular}
  \caption{Code and a plot side by side}
  \label{table:3}
\end{table}

>>>>

Code Environment types are summarized in Table~\ref{table:1}.

@@

% Code in Figures
\section{Code in Figure Environments}
A small example of code in a figure environment is demonstrated in Figure~\ref{code:example} (named CodeBlock~\ref{code:example} in the HTML). This is a common practice
in R News articles as it used to add a boxed border around the code which looks 
attractive. However, in web articles there isn't much advantage to it.

@@

Table~\ref{table:2} is an example of code environments within a table.

@@

A similar arrangement can be used to arrange figures/plots besides code environments.
Table~\ref{table:3} demonstrates a table with code and a figure.
\begin{table}[htbp]
  \centering
  \begin{tabular}{| c | c |}
  \hline
  Code & Plot\\
    \hline
    \begin{minipage}{0.45\textwidth}
\vspace{1mm}
\begin{example}
x <- 1:100
y <- dbinom(x,100,prob = 0.5)
plot(x,y)
\end{example}
    \end{minipage} &
    \begin{minipage}{0.45\textwidth}
    \centering
    \includegraphics[width=1\textwidth]{binom}
    \end{minipage}\\
    \hline
  \end{tabular}
  \caption{Code and a plot side by side}
  \label{table:3}
\end{table}
